Natural Stories

### 2021-07-05 Analysis/models.Rmd
more gam models

all_mean_data <- ngram_mean_data %>% union(grnn_mean_data) %>% union(txl_mean_data) %>% union(gpt_mean_data) %>% 
  select(surprisal, prev_surp,model) %>% 
  pivot_longer(cols=`surprisal`:`prev_surp`) %>% 
  mutate(s=ifelse(name=="surprisal", "Current","Previous"))
```

@@

```{r meaned data}
gam_ngram_1 <- gam(formula_interact, data=ngram_mean_data, method="REML")
gam_grnn_1 <- gam(formula_interact, data=grnn_mean_data, method="REML")
gam_txl_1 <- gam(formula_interact, data=txl_mean_data, method="REML")
gam_gpt_1 <- gam(formula_interact, data=gpt_mean_data, method="REML")

@@

```{r anovas}

@@

```{r plots}
plot(gam_gpt_1)
```

@@

a <- get_gam_predictions(model=gam_ngram_1, series=surprisal, series_length=100) %>% select(surprisal, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="5-gram", s="Current")
b <- get_gam_predictions(model=gam_ngram_1, series=prev_surp, series_length=100) %>% select(surprisal=prev_surp, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="5-gram", s="Previous")
c <- get_gam_predictions(model=gam_grnn_1, series=surprisal, series_length=100) %>% select(surprisal, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="GRNN", s="Current")
d <- get_gam_predictions(model=gam_grnn_1, series=prev_surp, series_length=100) %>% select(surprisal=prev_surp, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="GRNN", s="Previous")
e <- get_gam_predictions(model=gam_txl_1, series=surprisal, series_length=100) %>% select(surprisal, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="TXL", s="Current")
f <- get_gam_predictions(model=gam_txl_1, series=prev_surp, series_length=100) %>% select(surprisal=prev_surp, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="TXL", s="Previous")
```

```{r, eval=F}
all <- a %>% union(b) %>% union(c) %>% union(d) %>% union(e) %>% union(f) %>% write_rds("gam_predictions.rds")

gam1 <-  ggplot(all, aes(x=surprisal, y=rt, ymin=CI_lower, ymax=CI_upper))+
  geom_line()+
  geom_ribbon(alpha=.3)+
   #geom_density(data=all_data, aes(x=value), fill="gray",)+
  facet_grid(s~model)+
  coord_cartesian(ylim=c(700,1300), xlim=c(0,28))+
  labs(x="Surprisal (bits)", y="Reaction Time (ms)")+theme(axis.ticks.x=element_blank(), axis.title.x=element_blank(), axis.text.x=element_blank(), plot.margin=margin(t=0,r=0,b=0,l=0,unit="pt"))

dens2 <-   ggplot(all_data, aes(x=value))+
  geom_density(fill="gray",)+
  facet_grid(.~model)+
  labs(x="Surprisal (bits)", y="")+
  theme(axis.text.y = element_blank(), strip.text=element_blank(), axis.ticks.y =element_blank(), axis.title.y=element_blank(), panel.grid=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "cm"))

bot <- plot_grid(NA, dens2, NA, nrow=1, rel_widths = c(.16, 1, .08))

 plot_grid(gam1, bot, nrow=2, rel_heights = c(1, .3))

ggsave("../Papers/gam.pdf", width=4, height=2.3, unit="in")

@@

```{r first-story}
# to make things more comparable, only look at the first story each participant read

@@

# SPR GAMs
TODO

@@

all_data <- ngram_data %>% union(grnn_data) %>% union(txl_data) %>% union(gpt_data) %>% 
  write_rds("maze_pre_brms.rds")

@@

data=readRDS("maze_pre_brms.rds")
 priors <- c(
      set_prior("normal(1000, 1000)", class="Intercept"),
      set_prior("normal(0, 500)", class="b"),
      set_prior("normal(0, 500)", class="sd"),
      set_prior("lkj(1)",       class="cor"))
run_model <- function(model_spec,data,file_name){
  d <- data %>% filter(model==model_spec)
  m1 <- brm(rt ~ surprisal * len + freq * len +
              prev_surp * prev_len + prev_freq * prev_len+
              (surprisal * len + freq * len +
              prev_surp * prev_len + prev_freq * prev_len|subject)+(1|Word_ID),
            data=d,
            file=file_name,
            prior=priors,
            control=list(adapt_delta=.95))
}

@@

@@

all_spr <- ngram_data %>% union(grnn_data) %>% union(txl_data) %>% union(gpt_data) %>% 
  write_rds("spr_pre_brms.rds")
```

```{r spr lms, eval=F}

run_lm <- function(data,modelspec){
  d <- data %>% filter(model==modelspec)
model_1 <- lmer(rt ~ surp_center * length_center + length_center * freq_center +
                  past_surp_center * past_length_center + past_length_center * past_freq_center + 
                 past2_surp_center * past2_length_center + past2_length_center * past2_freq_center + 
                  past3_surp_center * past3_length_center + past3_length_center * past3_freq_center + 
                  (1|subject)+(1|Word_ID), data=d)
return(model_1)
}

m_ngram <- run_lm(all_spr,"5-gram")
m_grnn <- run_lm(all_spr, "GRNN")
m_txl <- run_lm(all_spr,"TXL")
m_gpt <- run_lm(all_spr,"GPT-2")

@@

>>>>

all_mean_data <- ngram_mean_data %>% union(grnn_mean_data) %>% union(txl_mean_data) %>% union(gpt_mean_data) %>% 
  select(surprisal, prev_surp,model) %>% 
  pivot_longer(cols=`surprisal`:`prev_surp`) %>% 
  mutate(s=ifelse(name=="surprisal", "Current","Previous")) %>% write_rds(here("Analysis/models/meaned_maze.rds"))
```

@@

```{r meaned data, eval=F}
gam_ngram_1 <- gam(formula_interact, data=ngram_mean_data, method="REML")
gam_grnn_1 <- gam(formula_interact, data=grnn_mean_data, method="REML")
gam_txl_1 <- gam(formula_interact, data=txl_mean_data, method="REML")
gam_gpt_1 <- gam(formula_interact, data=gpt_mean_data, method="REML")

@@

```{r anovas, eval=F}

@@

```{r plots, eval=F}
plot(gam_gpt_1)
```

@@

a <- get_gam_predictions(model=gam_ngram_1, series=surprisal, series_length=100) %>% select(surprisal, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="5-gram", s="Current")
b <- get_gam_predictions(model=gam_ngram_1, series=prev_surp, series_length=100) %>% select(surprisal=prev_surp, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="5-gram", s="Previous")
c <- get_gam_predictions(model=gam_grnn_1, series=surprisal, series_length=100) %>% select(surprisal, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="GRNN", s="Current")
d <- get_gam_predictions(model=gam_grnn_1, series=prev_surp, series_length=100) %>% select(surprisal=prev_surp, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="GRNN", s="Previous")
e <- get_gam_predictions(model=gam_txl_1, series=surprisal, series_length=100) %>% select(surprisal, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="TXL", s="Current")
f <- get_gam_predictions(model=gam_txl_1, series=prev_surp, series_length=100) %>% select(surprisal=prev_surp, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="TXL", s="Previous")
g <- get_gam_predictions(model=gam_gpt_1, series=surprisal, series_length=100) %>% select(surprisal, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="GPT-2", s="Current")
h <- get_gam_predictions(model=gam_gpt_1, series=prev_surp, series_length=100) %>% select(surprisal=prev_surp, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="GPT-2", s="Previous")
all <- a %>% union(b) %>% union(c) %>% union(d) %>% union(e) %>% union(f) %>% union(g) %>% union(h) %>% 
  mutate(model=factor(model, levels=c("5-gram", "GRNN", "TXL","GPT-2"))) %>% 
                        write_rds(here("Analysis/models/gam_predictions.rds"))
```

gam1 <- read_rds(here("Analysis/models/gam_predictions.rds")) %>%  ggplot( aes(x=surprisal, y=rt, ymin=CI_lower, ymax=CI_upper))+
  geom_line()+
  geom_ribbon(alpha=.3)+
  #facet_grid(s~model, scales="free_y")+
  facet_grid(s~model)+
  coord_cartesian(xlim=c(0,28))+
  labs(x="Surprisal (bits)", y="Reaction Time (ms)")+theme(axis.ticks.x=element_blank(), axis.title.x=element_blank(), axis.text.x=element_blank(), plot.margin=margin(t=0,r=0,b=0,l=0,unit="pt"))

dens2 <-   ggplot(all_mean_data, aes(x=value))+
  geom_density(fill="gray",)+
  facet_grid(.~model)+
  labs(x="Surprisal (bits)", y="")+
    coord_cartesian(xlim=c(0,28))+
  theme(axis.text.y = element_blank(), strip.text=element_blank(), axis.ticks.y =element_blank(), axis.title.y=element_blank(), panel.grid=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "cm"))

p2 = cowplot::align_plots(gam1, dens2, align = "v", axis="lr")
plot_grid(p2[[1]], p2[[2]], nrow=2, rel_heights = c(1, .3))

@@

```{r first-story, eval=F}
# to make things more comparable, only look at the first story each participant read

@@

# SPR GAMs

```{r for spr gam, eval=F}

ngram_mean_spr <- item_mean_spr %>% rename_with(~str_replace_all(.x, "ngram_", ""))%>%
  select(rt, surp, freq_center, length_center,
         past_surp, past_freq_center, past_length_center,
         past2_surp, past2_freq_center, past2_length_center,
         past3_surp, past3_freq_center, past3_length_center) %>% mutate(model="5-gram")

grnn_mean_spr <- item_mean_spr %>% rename_with(~str_replace_all(.x, "grnn_", ""))%>%
  select(rt, surp, freq_center, length_center,
         past_surp, past_freq_center, past_length_center,
         past2_surp, past2_freq_center, past2_length_center,
         past3_surp, past3_freq_center, past3_length_center) %>% mutate(model="GRNN")

txl_mean_spr <- item_mean_spr %>% rename_with(~str_replace_all(.x, "txl_", ""))%>%
  select(rt, surp, freq_center, length_center,
         past_surp, past_freq_center, past_length_center,
         past2_surp, past2_freq_center, past2_length_center,
         past3_surp, past3_freq_center, past3_length_center) %>% mutate(model="TXL")

gpt_mean_spr<-item_mean_spr %>% rename_with(~str_replace_all(.x, "gpt_", ""))%>%
  select(rt, surp, freq_center, length_center,
         past_surp, past_freq_center, past_length_center,
         past2_surp, past2_freq_center, past2_length_center,
         past3_surp, past3_freq_center, past3_length_center) %>% mutate(model="GPT-2")

all_mean_spr <- ngram_mean_spr %>% union(grnn_mean_spr) %>% union(txl_mean_spr) %>% union(gpt_mean_spr) %>% 
  select(surp, past_surp, past2_surp, past3_surp,model) %>% 
  pivot_longer(cols=`surp`:`past3_surp`) %>% 
  mutate(s=ifelse(name=="surprisal", "Current","Previous")) %>% write_rds(here("Analysis/models/meaned_spr.rds"))
```

```{r formulae, echo=T}
#no hierarchical, has freq x len interaction
spr_formula_interact <- rt ~ s(surp, bs="cr", k=20)+
                     ti(length_center, bs="cr")+
                     ti(freq_center,length_center, bs="cr")+
                     s(past_surp, bs="cr", k=20)+
                     ti(past_freq_center, bs="cr")+
                     ti(past_length_center, bs="cr")+
                     ti(past_freq_center, past_length_center, bs="cr")+
                     s(past2_surp, bs="cr", k=20)+
                     ti(past2_freq_center, bs="cr")+
                     ti(past2_length_center, bs="cr")+
                     ti(past2_freq_center, past2_length_center, bs="cr")+
                     s(past3_surp, bs="cr", k=20)+
                     ti(past3_freq_center, bs="cr")+
                     ti(past3_length_center, bs="cr")+
                     ti(past3_freq_center, past3_length_center, bs="cr")

```{r spr meaned data, eval=F}
gam_ngram_1 <- gam(spr_formula_interact, data=ngram_mean_spr, method="REML")
gam_grnn_1 <- gam(spr_formula_interact, data=grnn_mean_spr, method="REML")
gam_txl_1 <- gam(spr_formula_interact, data=txl_mean_spr, method="REML")
gam_gpt_1 <- gam(spr_formula_interact, data=gpt_mean_spr, method="REML")

```{r plot-gam-spr, eval=F}

a <- get_gam_predictions(model=gam_ngram_1, series=surp, series_length=100) %>% select(surprisal=surp, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="5-gram", s="Current")
b <- get_gam_predictions(model=gam_ngram_1, series=past_surp, series_length=100) %>% select(surprisal=past_surp, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="5-gram", s="Previous")
c <- get_gam_predictions(model=gam_ngram_1, series=past2_surp, series_length=100) %>% select(surprisal=past2_surp, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="5-gram", s="2Previous")
d <- get_gam_predictions(model=gam_ngram_1, series=past3_surp, series_length=100) %>% select(surprisal=past3_surp, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="5-gram", s="3Previous")

e <- get_gam_predictions(model=gam_grnn_1, series=surp, series_length=100) %>% select(surprisal=surp, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="GRNN", s="Current")
f <- get_gam_predictions(model=gam_grnn_1, series=past_surp, series_length=100) %>% select(surprisal=past_surp, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="GRNN", s="Previous")
g <- get_gam_predictions(model=gam_grnn_1, series=past2_surp, series_length=100) %>% select(surprisal=past2_surp, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="GRNN", s="2Previous")
h <- get_gam_predictions(model=gam_grnn_1, series=past3_surp, series_length=100) %>% select(surprisal=past3_surp, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="GRNN", s="3Previous")

i <- get_gam_predictions(model=gam_txl_1, series=surp, series_length=100) %>% select(surprisal=surp, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="TXL", s="Current")
j <- get_gam_predictions(model=gam_txl_1, series=past_surp, series_length=100) %>% select(surprisal=past_surp, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="TXL", s="Previous")
k <- get_gam_predictions(model=gam_txl_1, series=past2_surp, series_length=100) %>% select(surprisal=past2_surp, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="TXL", s="2Previous")
l <- get_gam_predictions(model=gam_txl_1, series=past3_surp, series_length=100) %>% select(surprisal=past3_surp, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="TXL", s="3Previous")

m <- get_gam_predictions(model=gam_gpt_1, series=surp, series_length=100) %>% select(surprisal=surp, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="GPT-2", s="Current")
n <- get_gam_predictions(model=gam_gpt_1, series=past_surp, series_length=100) %>% select(surprisal=past_surp, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="GPT-2", s="Previous")
o <- get_gam_predictions(model=gam_gpt_1, series=past2_surp, series_length=100) %>% select(surprisal=past2_surp, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="GPT-2", s="2Previous")
p <- get_gam_predictions(model=gam_gpt_1, series=past3_surp, series_length=100) %>% select(surprisal=past3_surp, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="GPT-2", s="3Previous")

all <- a %>% union(b) %>% union(c) %>% union(d) %>% union(e) %>% union(f) %>% union(g) %>% union(h) %>% 
   union(i) %>% union(j) %>% union(k) %>% union(l) %>% union(m) %>% union(n) %>% union(o) %>% union(p) %>% 
  mutate(model=factor(model, levels=c("5-gram", "GRNN", "TXL","GPT-2")),
         s=factor(s, levels=c("Current", "Previous", "2Previous", "3Previous"))) %>% 
                        write_rds(here("Analysis/models/spr_gam_predictions.rds"))
```

```{r, eval=T}

gam1 <- read_rds(here("Analysis/models/spr_gam_predictions.rds")) %>%  ggplot( aes(x=surprisal, y=rt, ymin=CI_lower, ymax=CI_upper))+
  geom_line()+
  geom_ribbon(alpha=.3)+
  facet_grid(s~model)+
  coord_cartesian(xlim=c(0,28))+
  labs(x="Surprisal (bits)", y="Reaction Time (ms)")+theme(axis.ticks.x=element_blank(), axis.title.x=element_blank(), axis.text.x=element_blank(), plot.margin=margin(t=0,r=0,b=0,l=0,unit="pt"))

dens2 <-   ggplot(all_mean_spr, aes(x=value))+
  geom_density(fill="gray",)+
  facet_grid(.~model)+
  labs(x="Surprisal (bits)", y="")+
    coord_cartesian(xlim=c(0,28))+
  theme(axis.text.y = element_blank(), strip.text=element_blank(), axis.ticks.y =element_blank(), axis.title.y=element_blank(), panel.grid=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "cm"))

p2 = cowplot::align_plots(gam1, dens2, align = "v", axis="lr")
plot_grid(p2[[1]], p2[[2]], nrow=2, rel_heights = c(1, .3))

@@

all_data <- ngram_data %>% union(grnn_data) %>% union(txl_data) %>% union(gpt_data) %>% 
  write_rds(here("Analysis/models/maze_pre_brms.rds"))

@@

```{r run brms, eval=F}
# Note this was actually run on a cluster with a separate script that just had this
data=readRDS("maze_pre_brms.rds")
 priors <- c(
      set_prior("normal(1000, 1000)", class="Intercept"),
      set_prior("normal(0, 500)", class="b"),
      set_prior("normal(0, 500)", class="sd"),
      set_prior("lkj(1)",       class="cor"))
run_model <- function(model_spec,data,file_name){
  d <- data %>% filter(model==model_spec)
  m1 <- brm(rt ~ surprisal * len + freq * len +
              prev_surp * prev_len + prev_freq * prev_len+
              (surprisal * len + freq * len +
              prev_surp * prev_len + prev_freq * prev_len|subject)+(1|Word_ID),
            data=d,
            file=file_name,
            prior=priors,
            control=list(adapt_delta=.95))
}

@@

```{r summary}

show_summary <- function(model){
  intervals <- gather_draws(model, `b_.*`, regex=T) %>% mean_qi()

  stats <- gather_draws(model, `b_.*`, regex=T) %>% 
    mutate(above_0=ifelse(.value>0, 1,0)) %>% 
    group_by(.variable) %>% 
    summarize(pct_above_0=mean(above_0)) %>% 
    mutate(`P` = signif(2*pmin(pct_above_0,1-pct_above_0), digits=2)) %>% 
    left_join(intervals, by=".variable") %>% 
    mutate(lower=round(.lower, digits=1),
           upper=round(.upper, digits=1),
           E=round(.value, digits=1),
           `Estimate`=str_c(E," [",lower,", ", upper,"]"),
           Term=str_sub(.variable, 3, -1),
           ) %>% 
    select(Term, `Estimate`)

  stats
}
```

```{r process-maze-models, eval=F}
ngram <- read_rds(here("Analysis/models/5-gram_maze.rds")) %>% show_summary() %>% mutate(model="5-gram")
txl <- read_rds(here("Analysis/models/txl_maze.rds")) %>% show_summary() %>% mutate(model="TXL")
grnn <- read_rds(here("Analysis/models/grnn_maze.rds")) %>% show_summary() %>% mutate(model="GRNN")
gpt <- read_rds(here("Analysis/models/gpt_maze.rds")) %>% show_summary() %>% mutate(model="GPT-2")

summ <- ngram %>% union(txl) %>% union(grnn) %>% union(gpt) %>% write_rds(here("Analysis/models/brms_maze_summ.rds"))

@@

all_spr <- ngram_data %>% union(grnn_data) %>% union(txl_data) %>% union(gpt_data) %>% 
  write_rds(here("Analysis/models/spr_pre_brms.rds"))

ngram_mean_data <- item_mean_spr %>% rename_with(~str_replace_all(.x, "ngram", "surp"))%>% 
  select(rt, surp_center, freq_center, length_center,
         past_surp_center, past_freq_center, past_length_center,
         past2_surp_center, past2_freq_center, past2_length_center,
         past3_surp_center, past3_freq_center, past3_length_center, Word_ID) %>% mutate(model="5-gram")

grnn_mean_data <- item_mean_spr %>% rename_with(~str_replace_all(.x, "grnn", "surp"))%>% 
  select(rt, surp_center, freq_center, length_center,
         past_surp_center, past_freq_center, past_length_center,
         past2_surp_center, past2_freq_center, past2_length_center,
         past3_surp_center, past3_freq_center, past3_length_center, Word_ID)%>% mutate(model="GRNN")

txl_mean_data <- item_mean_spr %>% rename_with(~str_replace_all(.x, "txl", "surp"))%>% 
  select(rt, surp_center, freq_center, length_center,
         past_surp_center, past_freq_center, past_length_center,
         past2_surp_center, past2_freq_center, past2_length_center,
         past3_surp_center, past3_freq_center, past3_length_center, Word_ID) %>% mutate(model="TXL")

gpt_mean_data <-item_mean_spr %>% rename_with(~str_replace_all(.x, "txl", "surp"))%>% 
  select(rt, surp_center, freq_center, length_center,
         past_surp_center, past_freq_center, past_length_center,
         past2_surp_center, past2_freq_center, past2_length_center,
         past3_surp_center, past3_freq_center, past3_length_center, Word_ID) %>% mutate(model="GPT-2")

all_mean_spr <- ngram_mean_data %>% union(grnn_mean_data) %>% union(txl_mean_data) %>% union(gpt_mean_data)

@@

```{r spr lms-mean, eval=T}

run_lm <- function(data,modelspec){
  d <- data %>% filter(model==modelspec)
model_1 <- lmer(rt ~ surp_center * length_center + length_center * freq_center +
                  past_surp_center * past_length_center + past_length_center * past_freq_center + 
                 past2_surp_center * past2_length_center + past2_length_center * past2_freq_center + 
                  past3_surp_center * past3_length_center + past3_length_center * past3_freq_center +(1|Word_ID), data=d)
return(model_1)
}

m_ngram <- run_lm(all_mean_spr,"5-gram")
m_grnn <- run_lm(all_mean_spr, "GRNN")
m_txl <- run_lm(all_mean_spr,"TXL")
m_gpt <- run_lm(all_mean_spr,"GPT-2")

```{r lmsumm}
summary(m_ngram)
summary(m_grnn)
summary(m_txl)
summary(m_gpt)
```

### 2021-07-05 Analysis/nat_stories.Rmd
more gam models

first <- d.raw %>% 
  group_by(WorkerId,correct) %>% 
  mutate(num=row_number()) %>% 
  filter(num==1) %>% 
  select(-num) %>% 
  group_by(correct) %>% 
  tally() %>% 
  mutate(pct=n/sum(n)) %>% 
  mutate(source="SPR 1st") %>% 
  select(source,correct,pct)

all <- data_filt %>% select(subject, num_correct) %>% 
  unique() %>% 
  mutate(correct=num_correct) %>% 
   group_by(correct) %>% 
  tally() %>% 
  mutate(pct=n/sum(n)) %>% 
  mutate(source="all Maze") %>% 
  select(source,correct, pct)

some <- data_filt %>% select(subject, num_correct) %>% 
  unique() %>% 
  left_join(data_error_summ, by=c("subject", "num_correct")) %>% 
  filter(pct_correct>.8) %>% 
  mutate(correct=num_correct) %>% 
   group_by(correct) %>% 
  tally() %>% 
  mutate(pct=n/sum(n)) %>% 
  mutate(source="Maze >80% correct") %>% 
  select(source,correct, pct)

to_plot <- all %>% union(some) %>% union(all_spr) %>% union(first)

>>>>

first_spr <- d.raw %>% 
  group_by(WorkerId,correct) %>% 
  mutate(num=row_number()) %>% 
  filter(num==1) %>% 
  select(-num) %>% 
  group_by(correct) %>% 
  tally() %>% 
  mutate(pct=n/sum(n)) %>% 
  mutate(source="SPR 1st story") %>% 
  select(source,correct,pct)

all_maze <- data_filt %>% select(subject, num_correct) %>% 
  unique() %>% 
  mutate(correct=num_correct) %>% 
   group_by(correct) %>% 
  tally() %>% 
  mutate(pct=n/sum(n)) %>% 
  mutate(source="all Maze") %>% 
  select(source,correct, pct)

maze_bad <- data_filt %>% select(subject, num_correct) %>% 
  unique() %>% 
  left_join(data_error_summ, by=c("subject", "num_correct")) %>% 
  filter(pct_correct<.8) %>% 
  mutate(correct=num_correct) %>% 
   group_by(correct) %>% 
  tally() %>% 
  mutate(pct=n/sum(n)) %>% 
  mutate(source="<80% correct") %>% 
  select(source,correct, pct)

maze_good <- data_filt %>% select(subject, num_correct) %>% 
  unique() %>% 
  left_join(data_error_summ, by=c("subject", "num_correct")) %>% 
  filter(pct_correct>.8) %>% 
  mutate(correct=num_correct) %>% 
   group_by(correct) %>% 
  tally() %>% 
  mutate(pct=n/sum(n)) %>% 
  mutate(source=">80% correct") %>% 
  select(source,correct, pct)

to_plot <- all_maze %>% union(maze_bad) %>% union(maze_good)  %>% union(all_spr) %>% union(first_spr) %>% write_rds(here("Analysis/comp.rds"))
